### 2022-06-17 final_manuscript_no_markup.tex
add recent PDF

\begin{figure}[!h]
\centering
%ast: use Adobe Acrobat to add missing accessibility metadata to your PDF file. ask how to do this this when submitting - some edits to the PDF may be needed to add alt-text to the final version https://chi2021.acm.org/for-authors/presenting/papers/guide-to-an-accessible-submission#late
\pdftooltip{
\includegraphics[width=\textwidth]{figs/fig1.png}}{
%Alt-text for the figure to be included in the final PDF: Diagram of how the 10 rules are organized into three groups: foundation rules (Rules 1-3), design rules (Rules 4 to 9), and a continuity rule (Rule 10). The overall diagram depicts an arrow from left to right which contains all the rules. In the left column, under the first label" Foundation", there are three text boxes in light blue: "1. Vision", "2. Safe environment", and "3. Organizing Team". In the middle column, under the label "Design Rules" there are six light green boxes with Rules "4. Counter bias", "5. Virtual / hybrid", "6. Accessibility", "7. Language", "8. Communication",  "9. Finance". To the right, below the arrowhead labeled Continuity, is the Tenth Rule in a light pink box "10. Pass the torch".
}
\caption{Schematic diagram of the rules organized in three groups: foundation (Rules 1, 2, and 3), design (Rules 4 to 9), and continuity (Rule 10).}
\label{fig:diagram}
\end{figure}

@@

\begin{figure}[!h]
\centering
\pdftooltip{
\includegraphics[width=\textwidth]{figs/fig2.pdf}}{
}
\caption{Margot the marmot was the useR! 2021 mascot. To represent the global and inclusive nature of the conference, Margot was drawn using scarves representing the colors of diverse communities of practice that are part of the large R community and specific groups of people we wanted to support explicitly. From left to right: Margot wearing scarves with the colors of MiR (Minorities in R \url{https://mircommunity.com}), R-Ladies \url{https://rladies.org}, AfricaR \url{https://africa-r.org}, and the LGBTQIA+ and transgender communities. Margot was created by Francisco Etchart and is available under a CC-BY-NC-SA license (\url{https://github.com/useRconf/visuals-2021}).}
\label{fig:marmots}
\end{figure}
%alt-text for the figure, to be included in the final PDF: Five marmots with colorful scarves. From left to right: a marmot with a dark and light green scarf from the MiR community is watching her tablet, a marmot with the purple and gray scarf for R-Ladies is stepping on a rock and watches the horizon, a marmot with an orange and purple AfricaR scarf is sitting on a couch watching a film on her laptop with popcorn, a yogi marmot with a rainbow LGBTQIA+ scarf does the warrior pose on her blue mat, and finally, a marmot with a scarf with the pink, light blue and white color of the transgender pride flag waves her hand.

@@

>>>>

\begin{figure}[!h]
\centering
%ast: use Adobe Acrobat to add missing accessibility metadata to your PDF file. ask how to do this this when submitting - some edits to the PDF may be needed to add alt-text to the final version https://chi2021.acm.org/for-authors/presenting/papers/guide-to-an-accessible-submission#late
\pdftooltip{
\includegraphics[width=\textwidth]{figs/fig1.png}}{
%Alt-text for the figure to be included in the final PDF: Diagram of how the 10 rules are organized into three groups: foundation rules (Rules 1-3), design rules (Rules 4 to 9), and a continuity rule (Rule 10). The overall diagram depicts an arrow from left to right which contains all the rules. In the left column, under the first label" Foundation", there are three text boxes in light blue: "1. Vision", "2. Safe environment", and "3. Organizing Team". In the middle column, under the label "Design Rules" there are six light green boxes with Rules "4. Counter bias", "5. Virtual / hybrid", "6. Accessibility", "7. Language", "8. Communication",  "9. Finance". To the right, below the arrowhead labeled Continuity, is the Tenth Rule in a light pink box "10. Pass the torch".
}
\caption{Schematic diagram of the rules organized in three groups: foundation (Rules 1, 2, and 3), design (Rules 4 to 9), and continuity (Rule 10). See alt-text in the `Alternative text for figures' section.}
\label{fig:diagram}
\end{figure}

@@

\begin{figure}[!h]
\centering
\pdftooltip{
\includegraphics[width=\textwidth]{figs/fig2.pdf}}{
}
\caption{Margot the marmot was the useR! 2021 mascot. To represent the global and inclusive nature of the conference, Margot was drawn using scarves representing the colors of diverse communities of practice that are part of the large R community and specific groups of people we wanted to support explicitly. From left to right: Margot wearing scarves with the colors of MiR (Minorities in R \url{https://mircommunity.com}), R-Ladies \url{https://rladies.org}, AfricaR \url{https://africa-r.org}, and the LGBTQIA+ and transgender communities. Margot was created by Francisco Etchart and is available under a CC-BY-NC-SA license (\url{https://github.com/useRconf/visuals-2021}). See alt-text in the `Alternative text for figures' section.}
\label{fig:marmots}
\end{figure}
%alt-text for the figure, to be included in the final PDF: Five marmots with colorful scarves. From left to right: a marmot with a dark and light green scarf from the MiR community is watching her tablet, a marmot with the purple and gray scarf for R-Ladies is stepping on a rock and watches the horizon, a marmot with an orange and purple AfricaR scarf is sitting on a couch watching a film on her laptop with popcorn, a yogi marmot with a rainbow LGBTQIA+ scarf does the warrior pose on her blue mat, and finally, a marmot with a scarf with the pink, light blue and white color of the transgender pride flag waves her hand.

@@

\section*{Alternative text for the figures}

\textbf{Fig 1.} Diagram of the ten rules organized into three groups: foundation rules (Rules 1-3), design rules (Rules 4 to 9), and a continuity rule (Rule 10). The overall diagram depicts an arrow from left to right containing all the rules. In the left column, under the first label `Foundation', there are three text boxes in light blue: `1. Vision', `2. Safe environment', and `3. Organizing Team'. In the middle column, under the label `Design Rules' there are six light green boxes with Rules `4. Counter bias', `5. Virtual/hybrid', `6. Accessibility', `7. Language', `8. Communication', `9. Finance'. To the right, below the arrowhead labeled `Continuity', is the tenth Rule in a light pink box `10. Pass the torch'.

\textbf{Fig 2.}  Five `Margot the marmot' with colorful scarves. From left to right: a marmot with a dark and light green scarf of the MiR community is looking at her tablet, a marmot with the purple and gray scarf of R-Ladies is stepping on a rock and watches the horizon, a marmot with an orange and purple AfricaR scarf is sitting on a couch watching a film on her laptop with popcorn, a yogi marmot with a rainbow LGBTQIA+ scarf does the warrior pose on her blue mat, and finally, a marmot with a scarf with the pink, light blue and white color of the transgender pride 
flag waves her hand.
